---
title: "Assignment1"
author: "Sadeeq"
date: "9/23/2020"
output: html_document
---
#Question 1:
Is there a significant difference between the mean perceived satisfaction level of younger adults and older adults?

#Hypothesis:
Ho: The variance of older adults and younger adults on life perceived satisfaction are equal
H1: The variance of older adults and younger adults on life perceived satisfaction are not equal.

Alpha: 0.05

#Decision:
Reject the null hypothesis if the p-value is less than 0.05, accept if otherwise.

#Test:

```{r}
olderAdults<-c(45, 38, 52, 48, 25, 39, 51, 46, 55, 46)
youngerAdults<-c(34, 22, 15, 27, 37, 41, 24, 19, 26, 36)

paired_1<-t.test(olderAdults, youngerAdults, paired =FALSE)
paired_1
```
#Conclusion:
Since p-value (0.0004) is less than alpha (0.05), we reject the null hypothesis.



#Question 2:
Is there a significant difference between the mean weight of rats before and after the simulation?

#Hypothesis:
Ho: There is no significant difference between the mean weight of rats before and after the simulation?

H1:There is a significant difference between the mean weight of rats before and after the simulation?

Alpha: 0.05

#Decision
Reject Ho if p-value < 0.05, otherwise accept Ho.

#Test
```{r}
simulation<-c(12, 7, 3, 11, 8, 5, 14, 7, 9, 10)
noSimulation<-c(8, 7, 4, 14, 6, 7, 12, 5, 5, 8)

paired_1<-t.test(simulation, noSimulation, paired =TRUE)
paired_1

```

#Conclusion
Since p-value(0.2208) is greater than alpha(0.05), so we accept the null hypothesis.


```{r}
df1<-read.table("C:/Users/USER/Desktop/Semicolon/R/R_with_Hamid/data/Assignment.csv", header=T, dec=".", sep=",")
df1

```