---
title: "Correlation"
author: "Sadeeq"
date: "9/24/2020"
output: html_document
---
#Question1:

```{r}
dt<-read.csv("C:/Users/USER/Desktop/Semicolon/R/R_with_Hamid/data/highway_mpg.csv", header=T, dec=".", sep=",")
dt

corr<-cor(x=dt$cyl, y=dt$hwy)

library(ggplot2)
ggplot(dt, aes(x=cyl, y=hwy)) +geom_point() +geom_smooth() +labs(title="Relationship between CYL and HWY")

```
There exist a negative relationship between variables as x tends to increase, y decreases and vice versa.

#Question2:
```{r}
modl<- lm(hwy~cyl, data=dt)
summary(modl)

```
The output depicts that the linear equation is: y = 40.0190 - 2.8153(cyl) 

The  p-value of 2.2e-16 indicates that the Cyl has significant effect on Hwy, we can conclude that Regression is useful.

#Question3
The intercept is also significant at 5% level of significance.

To interprete the slope, for a unit increase in the Hwy, the Cyl decreases by 2.8153.

#Question4
The R-Squared is interpreted as the amount of variation of the dependent variable that can be explained by the independent variable. For the model, the 57.9% of the total variation in Hwy can be explained by the independent variable "Cyl"

```{r}
dt$Residuals<- modl$residuals
plot(modl)
```

From the Q-Q Plot, Normality of residuals has not been violated as the points on the residual plot lie closely to the line.

Constant variance assumption is met as there is no pattern of points in the residual vs Fitted plot.

Linear relationship between Hwy and Cyl, the assumption is not violated as there is a linear relationship between both variables