---
title: "Stats"
author: "Sadeeq"
date: "9/18/2020"
output: pdf_document
---

```{r}
df<-read.table("C:/Users/USER/Desktop/Semicolon/R/R_with_Hamid/data/AdescoGym.csv", header=T, dec=".", sep=",")

df
t.test(df$Income, mu=30000, alternative = "greater")
```

#Research Question
Is the mean age greater than 20?

#Hypothesis
Ho = Mean age is not greater than 20
H1= Mean age is greater than 20

#Level of Significance
Level of significance: 0.05

#Conclusion
The p-value < 2.2e-16, so it is less than 0.05, which is the alpha value.
Therefore, the null hypothesis may be rejected. The alternate hypothesis,
μA - μB ≠ 0, is true at the 95% confidence interval.



```{r}
df<-read.table("C:/Users/USER/Desktop/Semicolon/R/R_with_Hamid/data/AdescoGym.csv", header=T, dec=".", sep=",")
t.test(df$Age, mu=20, alternative = "greater")

```
Test of Equality of Variance

Ho: The variance of Male and Female income are equal
H1: The variance of the Male and Female Income are not equal.

Alpha: 0.05

Decision: Reject Ho if p-value is less than 0.05, accept if otherwise.
```{r}
df<-read.table("C:/Users/USER/Desktop/Semicolon/R/R_with_Hamid/data/AdescoGym.csv", header=T, dec=".", sep=",")
df

library(car)
leveneTest(df$Income~df$Gender)


```

Conclusion: Since the p-value of our leveneTest is less than 0.05, we reject the null hypothesis and conclude the variance of the 2 groups are not equal.

#Research Question:
Is there a significant difference between the mean income of male and female?

#Hypothesis
Ho: There is no significant difference between the mean income of male and female.
H1: There is a significant difference between the mean income of male and female.

Alpha: 0.05

#Decision
Reject the null hypothesis if the p-value is less than 0.05, accept if otherwise.

#Test
```{r}
t.test(df$Income~df$Gender, alternative="two.sided", var.equal=F)

```
#Conclusion: 
We reject the null hypothesis because the p-value is less than 0.05.



#Question
Is there a significant difference between the mean weight of participants before and after the treatment?

#Hypothesis
Ho: There is no significant difference between the mean weight of participants before and after the treatment?

H1:There is a significant difference between the mean weight of participants before and after the treatment?

Alpha: 0.05

#Decision
Reject Ho if p-value < 0.05, otherwise accept Ho.

#Test
```{r}
 pre<-c(239, 170, 182, 143, 141, 170, 160, 154, 185, 130)
 post<-c(362, 343, 330, 340, 314, 567, 292, 439, 312, 292)
  paired_1<-t.test(pre, post, paired=TRUE)
  paired_1

```
#Conclusion
The p-value is 6.09e-05, so it is less than 0.05, which is the alpha value.
Therefore, the null hypothesis may be rejected.


```{r}
ad<-read.table("C:/Users/USER/Desktop/Semicolon/R/R_with_Hamid/data/AdescoGym.csv", header=T, dec=".", sep=",")

ad
library(ggplot2)
ggplot(ad, aes(x=Age, y=Income))+ geom_point() +labs(title="Relationship between Income and Age")
```

```{r}
attach(ad)
```

```{r}
modl<-lm(Income~Age)
summary(modl)

```

```{r}
nd<-data.frame(Age=c(27,28))
predict.lm(modl, newdata = nd)

head(ad)

modl<-lm(Income~Age, data=ad)
summary(modl)

```
```{r}
nd<-data.frame(Age=c(27, 28))
predict.lm(modl, newdata=nd)

ad$Residuals <- modl$residuals
head(ad)

ggplot(ad, aes(x=Residuals))+geom_histogram()
```
```{r}

shapiro.test(ad$Residuals)
```